One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-10-19 draft_02_zhiyu01.tex

\bibliographystyle{apsrev4-1}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{xcolor}
 \usepackage{bm}
 \usepackage[]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {red},
    citebordercolor = {green},
}
 \begin{document}
 \title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

@@

\begin{figure*}
\subfigure[$t=0$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
\end{minipage}
}
\subfigure[$t=\frac{1}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=2-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{2}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{3}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
\end{minipage}
}\subfigure[$t=\frac{4}{5}T$]{
\begin{minipage}[b]{0.18\linewidth}
\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
\end{minipage}
}
\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
\label{fig:Breathingfrequency2_0}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps} 
\caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
\label{fig:Breathingfrequency2_1}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: {\color{red}{Red}} for $F_0$=2000; {\color{yellow}{Yellow}} for $F_0$=3000; {\color{green}{Green}} for $F_0$=10000;  {\color{blue}{Blue}} for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=200_pre.eps} 
\caption{energy of each particle, $F_0=200$}
\label{fig:thermalization6}

\includegraphics[scale=0.6]{ZhiyuPictures/10_23_N=10_single_particle_energy_F0=1000_pre.eps} 
\caption{energy of each particle, $F_0=1000$}
\label{fig:thermalization7}
\end{figure}

>>>>

\bibliographystyle{apsrev4-1}

\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{xcolor}
 \usepackage{bm}
 \usepackage[]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {red},
    citebordercolor = {green},
}
\usepackage{epstopdf}
 \begin{document}
 \title{One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

@@

\begin{figure*}
%\subfigure[$t=0$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
%\end{minipage}
%}
%\subfigure[$t=\frac{1}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/%stationary_frame_t=2-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{2}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{3}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{4}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
%\end{minipage}
%}
\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}

\caption{N=50,F0=100,E=50000. Upper(lower) five pictures are snapshot of the configuration of the cloud in the stationary(rotating) frame at t=$\frac{1}{5}T$, $\frac{2}{5}T$, $\frac{3}{5}T$, $\frac{4}{5}T$, $T$ respectively.}
\label{fig:Breathingfrequency2_0}
\end{figure*}

\begin{figure*}
%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=0T_rev.eps} 
%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=20T_rev.eps}
%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=40T_rev.eps} 
%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=60T_rev.eps}
%\includegraphics[scale=0.23]{ZhiyuPictures/10_18rotating_frame_t=80T_rev.eps}
\includegraphics[width=0.9\textwidth]{ZhiyuPictures/rotating_frame_t=0-80T.eps}  
\caption{the precession behavior of cloud viewed in the rotating frame in phase-space. $\frac{t}{T}=0,20,40,60,80$}
\label{fig:Breathingfrequency2_1}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: Red for $F_0$=2000; Yellow for $F_0$=3000; Green for $F_0$=10000;  Blue for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
\caption{energy of each particle, $F_0=200$}
\label{fig:thermalization6}

\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
\caption{energy of each particle, $F_0=1000$}
\label{fig:thermalization7}
\end{figure}
